Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-14 proposal/mprop.tex
Add programming languages to experimental design
Create bullet pointed list for work plan section

@@

>>>>

Implementation wise, we would like to develop the application that will
perform both scraping, extraction and inspection in either Go or Java
as I am the most proficient with these two programming languages.

@@

\begin{itemize}
  \item decide which repositories to use for data (e.g. Apache, Mozilla, Eclipse);
  \item create scraping/extraction/inspection tool using either Go or Java;
  \item decide which approach to use for detecting similar tickets (the two
    approaches are listed above) after testing them on the tickets retrieved
    with the application;
  \item collect data, run the analysis and decide which components have
    the biggest impact on creating high quality tickets;
  \item write abstract, introduction, related work;
  \item write methodology and how we conducted the experiment (collecting
    data, running analysis);
  \item write results, contributions and conclusion for the paper.
\end{itemize}
